Global well-being and mental health in the internet age

### 2023-05-30 ms.Rmd
Add reference

However, evidence for widespread harms of online technologies is limited. Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020]. Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2021], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006]. A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted. As a consequence, much of the evidence purporting to show that internet technology adoption is associated with broad changes in well-being and mental health, or even causes negative outcomes, remains equivocal [@dickson2018screen; @hawkesCMOReportUnable2019].

>>>>

However, evidence for widespread harms of online technologies is limited. Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020]. Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [ghaiLackSampleDiversity2023; @ghaiSocialMediaAdolescent2022], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006]. A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted. As a consequence, much of the evidence purporting to show that internet technology adoption is associated with broad changes in well-being and mental health, or even causes negative outcomes, remains equivocal [@dickson2018screen; @hawkesCMOReportUnable2019].
